How has the Brazilian Amazon been constructed as a problem:Presidential speeches and transnational politics since 1985

### 2022-09-16 Draft_September_2022/Full_draft_20220901.rmd
#distancein1000sofkilometers

```{r Figure 6, fig.cap="Logistic Regression predicted values", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified",
                    mx_cat != "Other Mixed-types") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
# model
model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_ei <- glm(EI_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sd <- glm(SD_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sov <- glm(sov_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
# Plot model
ama_model$"Environmental Conservation" = predict(model_logit_con, ama_model, type = "response")
ama_model$"Economic Integration" = predict(model_logit_ei, ama_model, type = "response")
ama_model$"Social Development" = predict(model_logit_sd, ama_model, type = "response")
ama_model$"National Sovereignty" = predict(model_logit_sov, ama_model, type = "response")
plot_loc <- ama_model %>% gather(key=p_c, value = pred, 22:24)
plot_loc$p_c <-factor(plot_loc$p_c, levels = c("Economic Integration",
                                               "Environmental Conservation",
                                               "Social Development"))
all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
  geom_jitter(alpha=1, size=1) +
  geom_smooth(size = .5, se=FALSE) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Distance from the Amazon (km)",
       y = "",
       title = "Predicted probability of each problem-construction as a function of\ndistance from the Amazon",
       subtitle="Sovereignty was removed because of statistical insignificance (table 1).", 
       caption = "Curves in the plots are estimated using loess method.") +
    theme_am() +
  theme(legend.position = "none")+
  facet_wrap(~p_c, ncol=3)

@@

@@

md <-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd,
                          model_logit_sov, digits = 10, 
                          dep.var.labels = c("Conservation", "Economic Integration",
                                             "Social Development", "Sovereignty"),
                          covariate.labels = c("Distance from the Amazon (km)",
                                               "Election year", "Yearly Deforestation",
                                               "Yearly   Inflation"), no.space = TRUE,
                          title = "Logistic Regressions Output")
```

>>>>

```{r Figure 6, fig.cap="Logistic Regression predicted values", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified",
                    mx_cat != "Other Mixed-types") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))

# model

model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_ei <- glm(EI_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sd <- glm(SD_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sov <- glm(sov_vs_all ~ km_to_manaus + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)

# Plot model
ama_model$"Environmental Conservation" = predict(model_logit_con, ama_model, type = "response")
ama_model$"Economic Integration" = predict(model_logit_ei, ama_model, type = "response")
ama_model$"Social Development" = predict(model_logit_sd, ama_model, type = "response")
ama_model$"National Sovereignty" = predict(model_logit_sov, ama_model, type = "response")
plot_loc <- ama_model %>% gather(key=p_c, value = pred, 22:24)
plot_loc$p_c <-factor(plot_loc$p_c, levels = c("Economic Integration",
                                               "Environmental Conservation",
                                               "Social Development"))
all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
  geom_jitter(alpha=1, size=1) +
  geom_smooth(size = .5, se=FALSE) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Distance from the Amazon (km)",
       y = "",
       title = "Predicted probability of each problem-construction as a function of\ndistance from the Amazon",
       subtitle="Sovereignty was removed because of statistical insignificance (table 1).", 
       caption = "Curves in the plots are estimated using loess method.") +
    theme_am() +
  theme(legend.position = "none")+
  facet_wrap(~p_c, ncol=3)

@@

```{r Models for Table, include=FALSE}

#models for table

ama_model$thousand_km<- ama_model$km_to_manaus/1000

model_logit_con2 <- glm(con_vs_all ~ thousand_km + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_ei2 <- glm(EI_vs_all ~ thousand_km + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sd2 <- glm(SD_vs_all ~ thousand_km + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)
model_logit_sov2 <- glm(sov_vs_all ~ thousand_km + election_year + def_year + AAI,
                   family=binomial(link = "logit"), data = ama_model)

@@

md <-stargazer::stargazer(model_logit_con2, model_logit_ei2, model_logit_sd2,
                          model_logit_sov2, digits = 10, 
                          dep.var.labels = c("Conservation", "Economic Integration",
                                             "Social Development", "Sovereignty"),
                          covariate.labels = c("Distance from the Amazon in 1000s of km",
                                               "Election year", "Yearly Deforestation",
                                               "Yearly   Inflation"), no.space = TRUE,
                          title = "Logistic Regressions Output")
```
